%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Md Sirajus}{Salayhin}{ % Your name
\jobtitle{Data Engineer |} % Your website, LinkedIn profile or other web address
salayhin.dlab@gmail.com | +8801833362458 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page


%------------------------------------------------
% Coursework
%------------------------------------------------
\section{SKILLS}
\subsection{Big Data}
• Data Warehousing \\
• Data Modeling \\
• Hadoop \\
• Spark \\
• Athena \\
• Hive \\
• Apache Airflow  \\

\subsection{Data Visualization}
• Data Studio \\
• Tableau \\
• Redash \\
• Periscope Data \\

\subsection{Cloud Infrastructure}
• Amazon Web Services (AWS) \\
• Google Cloud Platform

\sectionspace % Some whitespace after the section

\subsection{Programming}
• Python, Golang, Ruby \\
• SQL \\
• Shell Script\\

\subsection{DATABASE}
• Google Big Query \\
• AWS Redshift, Redshift Spectrum  \\
• SQL Server 2016 \\
• MySQL , PostgraSQL, MongoDB
\sectionspace % Some whitespace after the section

\subsection{WEB}
• Ruby on Rails • Django • Flask

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Profiles} 
Github:// \href{https://github.com/salayhin}{\bf salayhin} \\
LinkedIn:// \href{https://www.linkedin.com/in/salayhin}{\bf salayhin} \\
StackOverflow:// \href{https://stackoverflow.com/users/717600/sirajus-salayhin}{\bf salayhin} \\
Twitter:// @salayhin
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------
\section{Education} 
\subsection{JAGANNATH UNIVERSITY}
\descript{B.SC IN PHYSICS}
\location{2008 | Dhaka, Bangladesh}

\sectionspace % Some whitespace after the section

\subsection{IICT, BUET}

\descript{POST GRADUATE DIPLOMA IN ICT}
\location{2019 | Dhaka, Bangladesh}
%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Pathao Ltd.}
\descript{| Senior Data Engineer Level II}

\location{June 2018 – Now | Dhaka, Bangladesh}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Data Lake & Data Warehouse Architect:
Designed and developed Data Lake and Data Warehouse in Google Cloud Storage and Google Big Query. This helped Pathao to build better data products and reporting tools.
\item Data Collection framework:
Developed data pipelines for data collection from different data sources using PySpark which runs on Google Cloud Service server-less cloud infrastructure called Dataproc.
\item Reporting and Visualisation:
Developed reporting framework which runs daily/ monthly/ quarterly to process a large amount of data on Google Big Query and send them automatically to different stakeholders. Also, design data models and prepare dashboards for different stakeholders on BI tools including Tableau/ Data Studio/ Redash.
\item Data Pipeline Monitoring Framework:
Developed data pipeline monitoring framework to verify source and destination data quality, Which includes total row counts, data types check, data schema check. This tool automatically sent alert to responsible stakeholders for any pipeline failure.
\item Infrastructure Management for Data Pipelines:
Worked as one of the primary maintainers of Data lake and data Warehouse Cloud Infrastructure. Built CI/CD pipelines deploy services. Built and integrated monitoring tools to visualize system health metrics. Also, Integrate Apache Airflow to manage data pipelines.
\item Data Access Control Policy:
Developed a data access control policy for Pathao. This helped my company to secure data within an organization and restrict any data breach from our data lake and data warehouse
\item Developed data integrity checking tool to ensure data integrity among source and destination
\item Tools & Technologies: Python, PySpark, Google Cloud Storage, Google Big Query, Google PubSub, Google Data Proc
\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{RELISOURCE TECHNOLOGIES LTD.}
\descript{| Senior Database Engineer}

\location{March 2018 – May 2018 | Dhaka, Bangladesh}
\begin{tightitemize}
\item Database Administrator:
Troubleshot architectural design with existing data warehouse and data integration pipelines. This involves data migration, replication, log shipping, database backup, etc.
\item Tools & Technologies: SQL Server, Redshift

\end{tightitemize}

\sectionspace % Some whitespace after the section

\runsubsection{AUGMEDIX INC.}
\descript{| SENIOR DATA ENGINEER}

\location{June 2015 – March 2018 | Dhaka, Bangladesh}
\begin{tightitemize}
\item Data Lake & Data Warehouse Architect:
Designed and developed Data Lake and Data Warehouse in S3 and SQL Server 2016. This helped Augmedix to build better data products and reporting tools.

\item Data Collection framework:
Developed data pipelines for data collection from different data sources including 3rd Party APIs, Google Spreadsheet, MySQL using Python, and Pentaho which runs on AWS Cloud Infrastructure.
\item Reporting and Visualisation:
Developed reporting framework which runs daily/ monthly/ quarterly to process a large amount of data on SQL Server and send them automatically to different stakeholders. Also, design data models and prepare dashboards for different stakeholders on BI tools including Tableau/ Sisense/ Periscope Data.
\item Tools & Technologies: R, Python, Pyspark, Pandas, Matplotlib,Jupyter Notebook, Django
\end{tightitemize}

\end{minipage} % The end of the right column


%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
\section{CERTIFICATES}
• \href{https://www.coursera.org/account/accomplishments/certificate/PB48PJLRP5VQ}{\bf Coursera: Introduction to Data Science in Python} \\
• \href{https://www.datacamp.com/courses/python-data-science-toolbox-part-1}{\bf Datacamp: Python Data Science Toolbox (Part 1) } \\
• \href{https://www.datacamp.com/courses/python-data-science-toolbox-part-2}{\bf Datacamp: Python Data Science Toolbox (Part 2) } \\
• \href{https://www.datacamp.com/courses/exploratory-data-analysis}{\bf Datacamp: Exploratory Data Analysis Using R
 }
\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Research
%------------------------------------------------

\section{EXPERIENCE}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{NASCENIA LTD.}
\descript{| RUBY ON RAILS DEVELOPER}

\location{June 2013 – June 2015 | Dhaka, Bangladesh}
\begin{tightitemize}
\item
\item B2B Marketplace:
Developed a marketplace application with multiple sellers, buyer for farmers, for the most unique, specialty foods from around the country (Ruby on Rails, MySQL)
\item Social Media Data Analytics:
Developed a web-based tool for social media data analysis and schedule social media posts. (Ruby on Rails, PostgreSQL)
\item Software as a Service:
Extend the functionality of a Web-based school management system software. (Ruby on Rails, PostgreSQL). Also partially developed a single web-based system for car dealers and traders to carry out their marketing, sales and purchasing activities. (Ruby on Rails, PostgreSQL)
\item Infrastructure Management:
Worked as one of the primary maintainers of software Cloud Infrastructure in AWS. Built CI/CD pipelines deploy services. Built and integrated monitoring tools to visualize system health metrics. 
\item Tools & Technologies: Ruby on Rails, PostgreSQL, MySQL, Apache Solr
\end{tightitemize}

\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------

\runsubsection{RIGHT BRAIN SOLUTION Ltd.}
\descript{| SOFTWARE ENGINEER}

\location{November 2011 – May 2013 | Dhaka, Bangladesh}
\sectionspace 
\begin{tightitemize}
\item Back End Service:
Developed API for a mobile application whose main functionality is friends, share local content, and discover new people! (Symfony 2, MongoDB)

\item Web Applications:
Developed an online rental shop for Fashion, shoes, skis, boot fitting, snowboard, accessories (Symfony 2, MySQL). Also worked as a team to develop one of the largest auto sites in Canada owned by Toronto Star. (WordPress, MySQL)

\item Business Process Automation Software:
Developed an online ticket management system for events. (Zend Framework, MySQL). Also developed an automated ERP solution for universities. It reduces workload and turns up the hectic working into smooth processing with the existing system. (Zend Framework, MySQL)

\item Tools & Technologies: Zend Framework, Symfony 2, Wordpress, MySQL, MongoDB
\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{NANOSOFT}
\descript{| PROGRAMMER}

\location{May 2011 – October 2011 | Dhaka, Bangladesh}
\begin{tightitemize}
\item Web Application:
Developed web-based application where officials of the Ministry of Power, Energy and Mineral Resources can add and manage their daily schedule. (Codeigniter, MySQL)
\item Tools & Technologies:Codeigniter,MySQL
\end{tightitemize}

%------------------------------------------------

\sectionspace % Some whitespace after the section
\end{minipage} % The end of the right column



\end{document}
